Fitness effects of mutations to SARS-CoV-2 proteins

### 2023-08-08 paper/paper.tex
made paragraph on last 5 kb of genome a bit more succinct

The accessory proteins are all encoded in the last third of the SARS-CoV-2 genome, meaning that our results show that this portion of the genome (with the exception of the nucleocapsid gene) is under relatively weak purifying selection (Figure~\ref{fig:effects_dist_position_order}).
This finding is consistent with observations that the genes encoded in the last third of the genome vary across coronaviruses~\citep{v2021coronavirus,llanes2020betacoronavirus}, and are mostly dispensable in cell culture~\citep{mcgrath2022sars,silvas2021contribution,liu2022live,liu2014accessory}.
This pattern of decreased purifying selection in genes encoded near the end of the genome is also observed in more distantly related orders of large single-stranded RNA viruses such as closteroviruses~\citep{wang2011genetic, dawson2013virus}.

>>>>

The accessory proteins are encoded in the last 5kb of the SARS-CoV-2 genome, meaning that our results show that this portion of the genome (with the exception of the genes coding for nucleoprotein, E, and M) is under relatively weak purifying selection (Figure~\ref{fig:effects_dist_position_order}).
Note that some accessory proteins also vary in presence/absence across coronaviruses~\citep{v2021coronavirus,llanes2020betacoronavirus}, and are mostly dispensable in cell culture~\citep{mcgrath2022sars,silvas2021contribution,liu2022live,liu2014accessory}.
Decreased purifying selection in genes encoded near the end of the genome is also observed in more distantly related orders of large single-stranded RNA viruses such as closteroviruses~\citep{wang2011genetic, dawson2013virus}.
